### 2023-03-16 chapters/paper_review/06_conclusions.tex
Change reference keys for review paper (WIP)

\item \textbf{Using the representation model.} So far, there are two main ways to use representation models: Freeze the representation models and use them as feature extractors, or fine-tune the representation models \edit{on} downstream tasks. 
\edit{Some efficient methods for leveraging SSL models exist in the NLP community. 
Adapters~\cite{pmlr-v97-houlsby19a,zaken2021bitfit,guo-etal-2021-parameter} are lightweight modules inserted into SSL models, and in downstream tasks, the parameters of SSL models are frozen, and only the adapters are trained. 
The prompt/instruction learning methods~\cite{liu2021pretrain} also freeze the SSL parameters and control the output of SSL by adding additional information, which is called \textit{prompt}, in the input.
Both adapter-based methods and prompt/instruction learning yield competitive performance compared with fine-tuning in NLP applications, but there is only little related work for speech~\cite{SpeechAdapter,SpeechPrompt}.
In addition, prompt for speech SSL does not achieve comparable performance on sequence generation tasks like phoneme recognition and slot filling, so how to use prompt is still an open question.}

@@

\item \textbf{Feature Disentanglement.} 
Speech SSL models show strengths on a surprisingly wide range of tasks~\cite{yang21c_interspeech}, suggesting that representations contain different information.
One way to further improve downstream tasks is to disentangle different information from the representation.
For example, we can decompose the representation into content embedding and speaker embedding and use content embedding for ASR and speaker embedding for SID.
Some work has been in this direction~\cite{pmlr-v162-qian22b,NANCY,MultimodelAmazonIS22}.

@@

\edit{\item \textbf{Capturing higher-level semantic information.} Although many representation learning approaches can go beyond low-level phonetic modeling to capture some lexical information~\cite{TuAnh_2022_discrete}, they still struggle in higher-level semantic tasks easily captured by word-level counterparts like BERT. One workaround is two-stage training~\cite{pGSLM, dialogue_GSLM}; however, this prevents propagating rich lexical and semantic knowledge modeled in the second stage to benefit the phonetically focused first stage. }

\item \textbf{Using text representation models to improve speech representation.} The amount of content information in speech corpora used to train speech representation models is far less than that of text representation models. Noting that the BERT training corpus exceeds 3 billion words~\cite{jacob2019BERT}, and assuming a typical speaking rate of 120 words per minute, a speech corpus containing the same content as the BERT training data would include 400,000 hours of audio, which exceeds the \edit{accumulated} training data of all current speech representation models. Therefore, to enable speech representation models to better learn human language, for instance by extracting semantic information from acoustic signals, the use of text models such as BERT and GPT  \edit{seems} key: nevertheless, how to use these to improve speech representation model pre-training remains an open question. 
%\edit{ There is already some study using both speech and text data to pre-training, but some paired data is still required to achieve good performance~\cite{bapna2021slam}.  }

>>>>

\item \textbf{Using the representation model.} So far, there are two main ways to use representation models: Freeze the representation models and use them as feature extractors, or fine-tune the representation models \edit{on} downstream tasks. 
\edit{Some efficient methods for leveraging SSL models exist in the NLP community. 
Adapters~\cite{pmlr-v97-houlsby19a,zaken2021bitfit,guo-etal-2021-parameter} are lightweight modules inserted into SSL models, and in downstream tasks, the parameters of SSL models are frozen, and only the adapters are trained. 
The prompt/instruction learning methods~\cite{liu_pretrain_2021} also freeze the SSL parameters and control the output of SSL by adding additional information, which is called \textit{prompt}, in the input.
Both adapter-based methods and prompt/instruction learning yield competitive performance compared with fine-tuning in NLP applications, but there is only little related work for speech~\cite{SpeechAdapter,SpeechPrompt}.
In addition, prompt for speech SSL does not achieve comparable performance on sequence generation tasks like phoneme recognition and slot filling, so how to use prompt is still an open question.}

@@

\item \textbf{Feature Disentanglement.} 
Speech SSL models show strengths on a surprisingly wide range of tasks~\cite{yang_superb_2021}, suggesting that representations contain different information.
One way to further improve downstream tasks is to disentangle different information from the representation.
For example, we can decompose the representation into content embedding and speaker embedding and use content embedding for ASR and speaker embedding for SID.
Some work has been in this direction~\cite{pmlr-v162-qian22b,NANCY,MultimodelAmazonIS22}.

@@

\edit{\item \textbf{Capturing higher-level semantic information.} Although many representation learning approaches can go beyond low-level phonetic modeling to capture some lexical information~\cite{TuAnh_2022_discrete}, they still struggle in higher-level semantic tasks easily captured by word-level counterparts like BERT. One workaround is two-stage training~\cite{kharitonov_textfree_2021, dialogue_nguyen_generative_2022}; however, this prevents propagating rich lexical and semantic knowledge modeled in the second stage to benefit the phonetically focused first stage. }

\item \textbf{Using text representation models to improve speech representation.} The amount of content information in speech corpora used to train speech representation models is far less than that of text representation models. Noting that the BERT training corpus exceeds 3 billion words~\cite{devlin_bert:_2018}, and assuming a typical speaking rate of 120 words per minute, a speech corpus containing the same content as the BERT training data would include 400,000 hours of audio, which exceeds the \edit{accumulated} training data of all current speech representation models. Therefore, to enable speech representation models to better learn human language, for instance by extracting semantic information from acoustic signals, the use of text models such as BERT and GPT  \edit{seems} key: nevertheless, how to use these to improve speech representation model pre-training remains an open question. 
%\edit{ There is already some study using both speech and text data to pre-training, but some paired data is still required to achieve good performance~\cite{bapna_slam_2021}.  }

### 2023-03-16 chapters/paper_review/main_hi.tex
Change reference keys for review paper (WIP)

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{Self-Training}}} \\
        IPL~\cite{xu2020iterative} & LL-60k & 4-gram + Transformer & 1.85 & 3.26 & 2.10 & 4.01 \\
        Noisy Student~\cite{park2020improved} & LV-60k & LSTM & 1.6 & 3.4 & 1.7 & 3.4 \\

>>>>

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{Self-Training}}} \\
        IPL~\cite{xu_iterative_2020} & LL-60k & 4-gram + Transformer & 1.85 & 3.26 & 2.10 & 4.01 \\
        Noisy Student~\cite{park_improved_2020} & LV-60k & LSTM & 1.6 & 3.4 & 1.7 & 3.4 \\

### 2023-03-16 chapters/paper_review/main_lo.tex
Change reference keys for review paper (WIP)

\begin{table*}[t]
    \centering
    \begin{tabular}{lcccccc}
        \toprule
        Model & Unlabeled Data & LM & dev-clean & dev-other & test-clean & test-other \\
        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{10-min labeled}}} \\
        % DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & - & - \\
        DiscreteBERT~\cite{baevski2019effectiveness} & LS-960 & 4-gram & 15.7 & 24.1 & 16.3 & 25.2 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 8.9 & 15.7 & 9.1 & 15.6 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & 4-gram & 6.3 & 9.8 & 6.6 & 10.3  \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 4.6 & 7.9 & 4.8 & 8.2 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 9.1 & 15.0 & 9.7 & 15.3  \\
        HUBERT \textsc{Large}   & LL-60k & 4-gram & 6.1 & 9.4 & 6.6 & 10.1 \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 4.3 & 7.0 & 4.7 & 7.6 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 4.4 & 6.1 & 4.6 & 6.8 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{1-hour labeled}}} \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 13.8 & 29.1 \\
        DiscreteBERT~\cite{baevski2019effectiveness} & LS-960 & 4-gram & 8.5 & 16.4 & 9.0 & 17.6 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 5.0 & 10.8 & 5.5 & 11.3 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 2.9 & 5.4 & 2.9 & 5.8 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 5.6 & 10.9 & 6.1 & 11.3  \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 2.6 & 4.9 & 2.9 & 5.4 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 2.6 & 4.2 & 2.8 & 4.8 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{10-hour labeled}}} \\
        SlimIPL~\cite{likhomanenko2020slimipl} & LS-960 & 4-gram + Transformer & 5.3 & 7.9 & 5.5 & 9.0 \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 5.4 & 13.3 \\
        DiscreteBERT~\cite{baevski2019effectiveness} & LS-960 & 4-gram & 5.3 & 13.2 & 5.9 & 14.1 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 3.8 & 9.1 & 4.3 & 9.5 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 2.4 & 4.8 & 2.6 & 4.9 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 3.9 & 9.0 & 4.3 & 9.4 \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 2.2 & 4.3 & 2.4 & 4.6 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 2.1 & 3.6 & 2.3 & 4.0 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{100-hour labeled}}} \\
        % LPM~\cite{hsu2020semi} & LL-60K & ConvLM & 4.87 & 13.84 & 4.88 & 15.28 \\
        IPL~\cite{xu2020iterative} & LL-60k & 4-gram + Transformer & 3.19 & 6.14 & 3.72 & 7.11 \\
        SlimIPL~\cite{likhomanenko2020slimipl} & LS-860 & 4-gram + Transformer & 2.2 & 4.6 & 2.7 & 5.2 \\
        Noisy Student\cite{park2020improved} & LS-860 & LSTM & 3.9 & 8.8 & 4.2 & 8.6 \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 5.0 & 12.1 \\
        DiscreteBERT~\cite{baevski2019effectiveness} & LS-960 & 4-gram & 4.0 & 10.9 & 4.5 & 12.1 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 2.7 & 7.9 & 3.4 & 8.0 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 1.9 & 4.0 & 2.0 & 4.0 \\

>>>>

\begin{table*}[t]
    \centering
    \begin{tabular}{lcccccc}
        \toprule
        Model & Unlabeled Data & LM & dev-clean & dev-other & test-clean & test-other \\
        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{10-min labeled}}} \\
        % DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & - & - \\
        DiscreteBERT~\cite{baevski_effectiveness_2020} & LS-960 & 4-gram & 15.7 & 24.1 & 16.3 & 25.2 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 8.9 & 15.7 & 9.1 & 15.6 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & 4-gram & 6.3 & 9.8 & 6.6 & 10.3  \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 4.6 & 7.9 & 4.8 & 8.2 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 9.1 & 15.0 & 9.7 & 15.3  \\
        HUBERT \textsc{Large}   & LL-60k & 4-gram & 6.1 & 9.4 & 6.6 & 10.1 \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 4.3 & 7.0 & 4.7 & 7.6 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 4.4 & 6.1 & 4.6 & 6.8 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{1-hour labeled}}} \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 13.8 & 29.1 \\
        DiscreteBERT~\cite{baevski_effectiveness_2020} & LS-960 & 4-gram & 8.5 & 16.4 & 9.0 & 17.6 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 5.0 & 10.8 & 5.5 & 11.3 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 2.9 & 5.4 & 2.9 & 5.8 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 5.6 & 10.9 & 6.1 & 11.3  \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 2.6 & 4.9 & 2.9 & 5.4 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 2.6 & 4.2 & 2.8 & 4.8 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{10-hour labeled}}} \\
        SlimIPL~\cite{likhomanenko2020slimipl} & LS-960 & 4-gram + Transformer & 5.3 & 7.9 & 5.5 & 9.0 \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 5.4 & 13.3 \\
        DiscreteBERT~\cite{baevski_effectiveness_2020} & LS-960 & 4-gram & 5.3 & 13.2 & 5.9 & 14.1 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 3.8 & 9.1 & 4.3 & 9.5 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 2.4 & 4.8 & 2.6 & 4.9 \\
        \midrule
        HUBERT \textsc{Base}    & LS-960 & 4-gram & 3.9 & 9.0 & 4.3 & 9.4 \\
        HUBERT \textsc{Large}   & LL-60k & Transformer & 2.2 & 4.3 & 2.4 & 4.6 \\
        HUBERT \textsc{X-Large} & LL-60k & Transformer & 2.1 & 3.6 & 2.3 & 4.0 \\

        \midrule\midrule
        \multicolumn{7}{c}{\textit{\textbf{100-hour labeled}}} \\
        % LPM~\cite{hsu2020semi} & LL-60K & ConvLM & 4.87 & 13.84 & 4.88 & 15.28 \\
        IPL~\cite{xu_iterative_2020} & LL-60k & 4-gram + Transformer & 3.19 & 6.14 & 3.72 & 7.11 \\
        SlimIPL~\cite{likhomanenko2020slimipl} & LS-860 & 4-gram + Transformer & 2.2 & 4.6 & 2.7 & 5.2 \\
        Noisy Student\cite{park_improved_2020} & LS-860 & LSTM & 3.9 & 8.8 & 4.2 & 8.6 \\
        DeCoAR 2.0~\cite{ling2020decoar} & LS-960 & 4-gram & - & - & 5.0 & 12.1 \\
        DiscreteBERT~\cite{baevski_effectiveness_2020} & LS-960 & 4-gram & 4.0 & 10.9 & 4.5 & 12.1 \\
        wav2vec 2.0 \textsc{Base}~\cite{baevski2020wav2vec}   & LS-960 & 4-gram & 2.7 & 7.9 & 3.4 & 8.0 \\
        wav2vec 2.0 \textsc{Large}~\cite{baevski2020wav2vec}  & LL-60k & Transformer & 1.9 & 4.0 & 2.0 & 4.0 \\

### 2023-03-16 chapters/paper_review/model.tex
Change reference keys for review paper (WIP)

Audio Word2vec \cite{Chung2016AudioWord2Vec}      & 2016 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\

VQ-VAE \cite{vqvae} & 2017 Nov. & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark \\ %2 Nov 2017

Speech2Vec \cite{chung2018speech2vec}     & 2018 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
Unspeech \cite{milde2018unspeech}         & 2018 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\

CPC \cite{oord2018representation}         & 2018 Jul. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\

PASE \cite{pascual2019learning}                   & 2019 Apr. & \cmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 6/4

APC \cite{chung2019unsupervised}          & 2019 Oct. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 5/4

wav2vec \cite{schneider2019wav2vec}       & 2019 Apr. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 11/4

vq-wav2vec \cite{Baevski2020vq-wav2vec} & 2019 Oct. & \xmark & \xmark & \cmark & \xmark & \cmark & \cmark & \xmark \\ %12 Oct 2019 %Lee: vq-wav2vec is CON or CLF??? %Lee: Discrete BERT use masking, but vq-wav2vec does not It is CON, not CLF.

Discrete BERT \cite{Baevski2020vq-wav2vec,baevski2019effectiveness} & 2019 Oct. & \xmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark \\ %12 Oct 2019 %10 Nov 2019 %In the paper of vq-wav2vec, it also includes the approach of Discrete BERT. I know this is tricky ....

Mockingjay  \cite{liu2020mockingjay}      & 2019 Oct. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 25/10-19

@@

PASE+ \cite{ravanelli2020multi}                & 2020 Jan. & \cmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 25/1 % I think contrastive always have learned target.

@@

VQ-APC \cite{chung20e_interspeech}  & 2020 May  & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark \\ %17/05

@@

TERA \cite{liu2021tera}                   & 2020 Jul. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 12/7

@@

wav2vec-C \cite{sadhu21_interspeech} & 2021 Mar. & \cmark & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark \\ %9 Mar 2021 %Lee:  consistency loss is reconstruction

HuBERT \cite{hsu2021hubert}               & 2021 Jun. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ % 14/6

W2v-bert \cite{w2vbert} & 2021 Aug & \xmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark \\
%7 Aug 2021

pMPC \cite{yue2021pMPC}  & 2021 Aug. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ %30 August – 3 September, 2021 (I do not find arXiv version.)

WavLM \cite{chen2021wavlm} & 2021 Oct. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ %26 Oct 2021

data2vec \cite{data2vec}     & 2022 Jan. & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark \\ % 20/1

@@

\begin{comment}
\begin{table*}[h!]
\caption{
The models are sorted according to the publication date of the first version on arXiv, which might differ from the year indicated by the citation. 
\textbc{{reg}} means that the model uses a regression loss, 
\textbc{{clf}} that it uses a classification loss,
\textbc{{con}} that it uses a contrastive loss, 
\textbc{{msk}} that it uses masking to define the target region, 
\textbc{{ltg}} that it uses a learned target, %lasseborgholt: We could consider using the inverse of this attribute. I.e., that the model uses the input as taget and belongs in the generative category.
\textbc{{qtz}} that it uses a quantized target, and
\textbc{{emb}} that it embeds a variable-length segment
}
\label{tab:model-taxonomy}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ l l | c c c | c c c | c } 
\toprule
\multicolumn{2}{c}{} & 
\multicolumn{3}{c}{\small\textsc{Loss}} & 
\multicolumn{3}{c}{\small\textsc{Target}} &
 \\
\textbc{{model}} &
\textbc{{pub. date}} &
\textbc{{reg}} & 
\textbc{{clf}} & 
\textbc{{con}} &
\textbc{{msk}} &
\textbc{{ltg}} &  
\textbc{{qtz}} & 
\textbc{{emb}} \\
\midrule
%                                                         REG      CLF      CON      MSK      LTG      QTZ      EMB  
Audio Word2vec \cite{Chung2016AudioWord2Vec}      & 2016 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
Speech2Vec \cite{chung2018speech2vec}     & 2018 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
% Unspeech \cite{milde2018unspeech}         & 2018 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
CPC \cite{oord2018representation}         & 2018 Jul. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\

PASE \cite{pascual2019learning}                   & 2019 Apr. & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark & \xmark \\ % 6/4

APC \cite{chung2019unsupervised}          & 2019 Oct. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 5/4
wav2vec \cite{schneider2019wav2vec}       & 2019 Apr. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 11/4
%VQ-APC \cite{chung2020vector}             & 2020 May  & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ 
Mockingjay  \cite{liu2020mockingjay}      & 2019 Oct. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 25/10-19
%DeCoAR \cite{ling2020deep}                & 2019 Dec. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 3/12-19
%PASE+ \cite{Ravanelli2020}                & 2020 Jan. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 25/1
wav2vec 2.0 \cite{baevski2020wav2vec}     & 2020 Jun. & \xmark & \xmark & \cmark & \cmark & \xmark & \cmark & \xmark \\ % 20/6
%TERA \cite{liu2021tera}                   & 2021 Jul. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 12/7

@@

DeCoAR 2.0 \cite{ling2020decoar}          & 2020 Dec. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 11/12
HuBERT \cite{hsu2021hubert}               & 2021 Jun. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ % 14/6
data2vec \cite{data2vec}     & 2022 Jan. & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark \\ % 20/1
\bottomrule
\end{tabular}
\end{center}
\end{table*}

>>>>

Audio Word2vec \cite{chung_audio_2016}      & 2016 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\

VQ-VAE \cite{oord_neural_2018} & 2017 Nov. & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark \\ %2 Nov 2017

Speech2Vec \cite{chung_speech2vec_2018}     & 2018 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
Unspeech \cite{milde2018unspeech}         & 2018 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\

CPC \cite{oord_representation_2018}         & 2018 Jul. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\

PASE \cite{pascual_learning_2019}                   & 2019 Apr. & \cmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 6/4

APC \cite{chung_unsupervised_2019}          & 2019 Oct. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 5/4

wav2vec \cite{schneider_wav2vec:_2019}       & 2019 Apr. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 11/4

vq-wav2vec \cite{baevski_vq-wav2vec_2020} & 2019 Oct. & \xmark & \xmark & \cmark & \xmark & \cmark & \cmark & \xmark \\ %12 Oct 2019 %Lee: vq-wav2vec is CON or CLF??? %Lee: Discrete BERT use masking, but vq-wav2vec does not It is CON, not CLF.

Discrete BERT \cite{baevski_vq-wav2vec_2020,baevski_effectiveness_2020} & 2019 Oct. & \xmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark \\ %12 Oct 2019 %10 Nov 2019 %In the paper of vq-wav2vec, it also includes the approach of Discrete BERT. I know this is tricky ....

Mockingjay  \cite{liu_mockingjay_2020}      & 2019 Oct. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 25/10-19

@@

PASE+ \cite{ravanelli_multi_2020}                & 2020 Jan. & \cmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 25/1 % I think contrastive always have learned target.

@@

VQ-APC \cite{chung_vector-quantized_2020}  & 2020 May  & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark \\ %17/05

@@

TERA \cite{liu_tera_2021}                   & 2020 Jul. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 12/7

@@

wav2vec-C \cite{sadhu_wav2vec-c_2021} & 2021 Mar. & \cmark & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark \\ %9 Mar 2021 %Lee:  consistency loss is reconstruction

HuBERT \cite{hsu_hubert_2021}               & 2021 Jun. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ % 14/6

W2v-bert \cite{chung_w2vbert_2021} & 2021 Aug & \xmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark \\
%7 Aug 2021

pMPC \cite{yue_pmpc_2021}  & 2021 Aug. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ %30 August – 3 September, 2021 (I do not find arXiv version.)

WavLM \cite{chen_wavlm_2021} & 2021 Oct. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ %26 Oct 2021

data2vec \cite{baevski_data2vec_2022}     & 2022 Jan. & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark \\ % 20/1

@@

\begin{comment}
\begin{table*}[h!]
\caption{
The models are sorted according to the publication date of the first version on arXiv, which might differ from the year indicated by the citation. 
\textbc{{reg}} means that the model uses a regression loss, 
\textbc{{clf}} that it uses a classification loss,
\textbc{{con}} that it uses a contrastive loss, 
\textbc{{msk}} that it uses masking to define the target region, 
\textbc{{ltg}} that it uses a learned target, %lasseborgholt: We could consider using the inverse of this attribute. I.e., that the model uses the input as taget and belongs in the generative category.
\textbc{{qtz}} that it uses a quantized target, and
\textbc{{emb}} that it embeds a variable-length segment
}
\label{tab:model-taxonomy}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ l l | c c c | c c c | c } 
\toprule
\multicolumn{2}{c}{} & 
\multicolumn{3}{c}{\small\textsc{Loss}} & 
\multicolumn{3}{c}{\small\textsc{Target}} &
 \\
\textbc{{model}} &
\textbc{{pub. date}} &
\textbc{{reg}} & 
\textbc{{clf}} & 
\textbc{{con}} &
\textbc{{msk}} &
\textbc{{ltg}} &  
\textbc{{qtz}} & 
\textbc{{emb}} \\
\midrule
%                                                         REG      CLF      CON      MSK      LTG      QTZ      EMB  
Audio Word2vec \cite{chung_audio_2016}      & 2016 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
Speech2Vec \cite{chung_speech2vec_2018}     & 2018 Mar. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
% Unspeech \cite{milde2018unspeech}         & 2018 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
CPC \cite{oord_representation_2018}         & 2018 Jul. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\

PASE \cite{pascual_learning_2019}                   & 2019 Apr. & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark & \xmark \\ % 6/4

APC \cite{chung_unsupervised_2019}          & 2019 Oct. & \cmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 5/4
wav2vec \cite{schneider_wav2vec:_2019}       & 2019 Apr. & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark \\ % 11/4
%VQ-APC \cite{chung2020vector}             & 2020 May  & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ 
Mockingjay  \cite{liu_mockingjay_2020}      & 2019 Oct. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 25/10-19
%DeCoAR \cite{ling2020deep}                & 2019 Dec. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 3/12-19
%PASE+ \cite{Ravanelli2020}                & 2020 Jan. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 25/1
wav2vec 2.0 \cite{baevski2020wav2vec}     & 2020 Jun. & \xmark & \xmark & \cmark & \cmark & \xmark & \cmark & \xmark \\ % 20/6
%TERA \cite{liu_tera_2021}                   & 2021 Jul. & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark & \xmark \\ % 12/7

@@

DeCoAR 2.0 \cite{ling2020decoar}          & 2020 Dec. & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\ % 11/12
HuBERT \cite{hsu_hubert_2021}               & 2021 Jun. & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark \\ % 14/6
data2vec \cite{baevski_data2vec_2022}     & 2022 Jan. & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark \\ % 20/1
\bottomrule
\end{tabular}
\end{center}
\end{table*}
